### 2019-07-12 report/chapter03.tex
Report based on the new data

\chapter{Results}

% 
% \section{Meta-analysis}
% The data at hand is composed of over 400,000 results with balanced sample size $n > 24$. The significance of the p-values of treatment effect estimates was calculated for all results in the dataset with acceptable sample size and outcome measures as odds ratios, peto odds ratios, risk ratios, risk differences and mean and standardized mean differences. 
% 
% %Significance over time? Chunck 1
% 
% The results that can be pooled are analysed by fixed-effects meta-analysis, random-effects meta-analysis and random-effects meta-analysis with Hartung-Knapp method.
% 
% \vspace{0mm}
% In the following, the results are combined with the results of their corresponding meta-analysis if possible (i.e. if studies were not unique in the dataset with respect to their experimental setup). The significance of the treatment effect (primary significance) in a single result is then compared to the significance of the pooled treatment effect (secondary significance). 
% In Figure \ref{primary.secondary.significance}, the overall fraction of studies with significant and non-significant meta-analysis results is shown. The meta-analysis method used to pool the treatment effect estimates and assessing significance is indicated on the right hand side of the Figure. The colors indicate the overall fraction of rejected or accepted null-hypotheses of no treatment effect.
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% #plot(sig.meta.c)
% @
% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis. The fractions have been calculated
% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
% \label{primary.secondary.significance}
% \end{figure}
% 
% What has been found is that even the meta-analysis that for all meta-analysis methods, the amount of secondary significance is higher than the amount of primary significance. Thus more primarily non-significant results can be attached to a secondarily significant result than vice-versa.
% 
% \vspace{0mm}
% To illustrate this, the fraction of studies with significant primary treatment effect and primary non-significant treatment effect can be plotted separately (Figure \ref{primary.secondary.significance.sep.sig}). 
% 
% \begin{figure}
% <<echo=FALSE, warning=FALSE>>=
% #grid.arrange(sig.meta.plot1, nonsig.meta.plot, ncol= 1)
% @
% \caption{Overall fraction of studies whose treatment effect estimate was significant when pooled by means of meta-analysis, separated by significance of study treatment effect estimate. The fractions have been calculated
% by fixed-effects, random-effects and Hartung and Knapp adjusted random-effects meta-analysis}
% \label{primary.secondary.significance}
% \end{figure}
% 
% It can be seen that the extent of overlap between primary and secondary significance varies between meta-analysis. A considerable amount of both primary significant and primary non-significant results are overruled by meta-analysis hypothesis tests. 
% 
% 
% The amount of significant heterogeneity in the results used by the meta-analyses is length(which(mly$sig.Q == 0)) and corresponds to (length(which(mly$sig.Q == 0))/ dim(mly)[1])*100\% of the total number of meta-analyses.
% 
% %Comparison of significance separated for significant Q? Chunck 2
% 
% %Proportion of significant pooled estimates based on proportion of single pooled estimates? Chunck 5

\section{Small study effects}

To provide an overview over the abundance of small study effects in the dataset, first it is shown how median absolute effect size decreases with increasing sample size of the results (Figure \ref{effect.samplesize}). 
%In some sense, this is the same idea as for a funnel plot, by depicting the size of effects relative to their variance.

\vspace{0mm}
A clear trend of decrease of absolute effect size with increasing sample size (i.e. smaller variance) is visible. 
%It is particularly substantive from very small trials ($n$ = 10) to medium sample size ($n$ = 100) and afterwards it evens off. With increasing sample size, there are fewer results, therefore, the variation between medians increases. 
All effects are normalized by subtracting the mean effect size of the dataset and dividing through the standard deviation. Note that various types of outcome measures are included, such as mean difference and risk ratios, and are normalized with respect to all effects.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-5-1}

}

\end{knitrout}
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size.}
\label{effect.samplesize}
\end{figure}

The median absolute normalized effect size can be visualized for the different outcome measures separately (Figure \ref{effect.samplesize.separated}). The plot confirms the trend of median effect size decrease towards lower sample size (e.g. for Risk Ratios: decrease $> 0.1$ standard deviations from 10 to 50 study participants). Instead of normalizing the effects 
%(i.e. subtracting mean and dividing through the standard deviation) 
for all effect sizes, the effects are normalized with respect to the effects of the same outcome measures.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-6-1}

}

\end{knitrout}
\caption{Median of the absolute value of the normalized effect size plotted against the total sample size, separated for outcome measures.}
\label{effect.samplesize.separated}
\end{figure}

%Show absolute effect size depending on scaled time? Chunck 3

\subsection{Small Study Effect Tests}

There are tests that can be applied to find out if small study effects are present in the meta analysis. For the precise description, see the methods section. Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = 1383)
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = 3955). The amount of studies varies from 5\% (Schwarzer's Test) to 13 \% (Egger's Test) for binary outcomes and 9\% (Begg and Mazumdar's Test) to 25 \% (Egger's Test) for continuous outcomes.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-8-1}

}

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-9-1}

}

\end{knitrout}
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

There is no substantive change in the fraction of positive test results, depending on if the pooled treatment effect size estimate is significant or not. Most substantively, the fraction of positive Egger Test results increases for significant pooled treatment effects by 0.1825716 (the minimal increase is -0.0032246 for Schwarzer's Test).

%Show plots of significant meta-analyses separated? Chunck 4

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year, such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-10-1}

}

\end{knitrout}
\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
\label{pub.bias.overtime}
\end{figure}

The agreement of the tests, i.e. the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types. Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%). Correlation varies more between tests, both for continuous and binary outcome tests.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue May 21 16:11:40 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
egger.schwarzer & 0.73 & 0.23 \\ 
  egger.peter & 0.75 & 0.37 \\ 
  egger.rucker & 0.75 & 0.34 \\ 
  egger.harbord & 0.79 & 0.51 \\ 
  schwarzer.peter & 0.81 & 0.26 \\ 
  schwarzer.rucker & 0.81 & 0.25 \\ 
  schwarzer.harbord & 0.86 & 0.47 \\ 
  rucker.peter & 0.87 & 0.64 \\ 
  harbord.peter & 0.84 & 0.50 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)} 
\label{agreement.bin}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue May 21 16:11:40 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
 & Test Agreement & P-value Correlation \\ 
  \hline
thomson.egger & 0.85 & 0.69 \\ 
  thomson.begg & 0.77 & 0.47 \\ 
  egger.begg & 0.73 & 0.36 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)} 
\label{agreement.cont}
\end{table}

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}. %(Suggests that 10 is likely too small)
In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test. A trend towards more rejections for larger sample sizes can be seen.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-13-1}

}

\end{knitrout}
\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
\label{pvalues.samplesize}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is 0.19 and the median 0.18. 
% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. 
In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-14-1}

}

\end{knitrout}
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
\label{trimfill.pvalues.bin}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-15-1}

}

\end{knitrout}
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
\label{trimfill.pvalues.cont}
\end{figure}

\subsection{Small Study Effect Correction}
Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate. Three of them will be applied to the meta-analyses shown previously that have ten or more study results and are therefore eligible for testing for publication bias.

\vspace{0mm}
The extent to what the results of the meta-analysis results are changed can be investigated. Because statistical significance is often used to decide if there is a treatment effect, a non-significant corrected effect size estimate can indicate that an observed treatment effect has been accepted because of small study effects. Therefore, the cases have been counted in which 
\begin{enumerate}
\item Significance or non-significance of pooled estimate of meta-analysis did not change after correction for small study effects.
\item Significance of pooled estimate of meta-analysis did change to non-significance after correction for small study effects.
\item Non-significance of pooled estimate of meta-analysis did change to significance after correction for small study effects.
\end{enumerate}

The results of this can be seen in Figure \ref{significance.change.fixed} for all three methods, comparing the significance of the corrected pooled effect size estimate with the significance of the pooled effect size estimate of the fixed effects meta-analysis. The same for significance of random effects meta-analysis is shown in Figure \ref{significance.change.random}. The significance threshold was chosen such that the $p$-value had to be < 0.05 for rejection of the null hypothesis of no treatment effect. The correction methods were trim-and-fill, copas selection model and regression with random effects and shrinkage of within-study-variance methods. More details to the applied correction methods and their application are in the methods section \ref{methods}. Notably, the correction methods has been applied to all meta-analyses, thus also for such that had no significant small study effect test result.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-16-1}

}

\end{knitrout}
\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction.}
\label{significance.change.fixed}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-17-1}

}

\end{knitrout}
\caption{Change in signficance of random effects meta-analysis pooled estimate after correction.}
\label{significance.change.random}
\end{figure}

Since it has been previously seen in Figure \ref{test.results} that the results of small study effects vary considerably between continuous outcomes, the results in significance change from fixed effects meta-analysis can be seen separately in Figure \ref{significance.change.fixed.sep} for continuous and binary outcomes. The change in significance from random effects meta-analysis to significance of corrected estimate can be seen in Figure \ref{significance.change.fixed.sep}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-18-1}

}

\end{knitrout}
\caption{Change in signficance of fixed effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
\label{significance.change.fixed.sep}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-19-1}

}

\end{knitrout}
\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
\label{significance.change.random}
\end{figure}

Because the real amount of publication bias in the dataset is not known, the correction method can also be applied only to meta-analyses that have publication bias according to the small study effect tests in the previous section. Because the test developed by \citet{thomson.sharp} has been applied to both binary and continuous outcome meta-analyses (in the case of binary outcomes to arcsine variance stabilized proportions), it is used as a criterium to distinguish biased from unbiased meta-analyses. The proportions of significance tests of pooled treatment effects that turned from significant to non-significant, non-significant to significant etc. are shown in Figure \ref{significance.change.fixed.sep}. Fixed effects meta-analysis has been used to determine signficance of the uncorrected estimate.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

{\centering \includegraphics[width=\textwidth-3cm]{figure/ch02_figunnamed-chunk-20-1}

}

\end{knitrout}
\caption{Change in signficance of random effects meta-analysis pooled estimate after correction, separated for continuous and binary outcomes.}
\label{significance.change.random}
\end{figure}

Similarly, the number of missing studies per meta-analysis, i.e. those which have not been included because of small study effects, are estimated by the copas and trim-and-fill method and their empirical distribution is shown in histograms in Figure \ref{missing.studies.distribution}. For visualisation, the fraction of unpublished studies from the total fraction of available studies is shown.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.98, 0.98, 0.98}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in arrange\_impl(.data, dots): Evaluation error: object 'Study' not found.}}\end{kframe}
\end{knitrout}

\chapter{The Cochrane Dataset} \label{ch:dataset}

\section{Cochrane Systematic Reviews}
The Cochrane Group has specialized on systematic reviews in clinical science. Certain knowledge of standards and principles of the Cochrane Group may help to assess the quality and the properties of the dataset. The following information stems from the Cochrane Handbook for Systematic Reviews \citep{cochrane.handbook}. \\
The definition of a systematic review is that it ``attempts to collate all empirical evidence that fits pre-specified eligibility criteria in order to answer a specific research question.'' Thus, the ``key properties of a review are'':

\begin{itemize}
\item``a clearly stated set of objectives with pre-defined eligibility criteria for studies''
\item ``an explicit, reproducible methodology''
\item ``a systematic search that attempts to identify all studies that would meet the eligibility criteria''
\item ``an assessment of the validity of the findings of the included studies, for example through the assessment of risk of bias''
\end{itemize}

At the end of a systematic review, ``a systematic presentation, and synthesis, of the characteristics and findings of the included studies'' is done. \\
53 Cochrane Review Groups prepare and maintain the reviews within specific areas of health care. A group consists of ``researchers, healthcare professionals and people using healthcare services (consumers)''. \\
The groups are supported by Method Groups, Centers and Fields. The Cochrane Method Groups aim to discuss and consult the groups in methodological questions concerning review preparation. The Centers play a main role in training and support of the Groups. The Fields are responsible for broad medical research areas and follow priorities in those areas by advice and control of the groups. \\
The first step in a review is writing a protocol, specifying the research question, the methods to be used in literature search and analysis and the eligibility criteria of the study. Changes in protocols are possible but have to be documented and the protocol is published in advance of the publication of the full review. The choices of methodology as well as the changes should not be made ``on the basis of how they affect the outcome of the research study''. \\
In order to avoid potential conflicts of interests, there is a code of conduct that all entities of the Cochrane Organization have to agree on: conflicts of interest must be disclosed and possibly be forwarded to the Cochrane Center, and participation of review authors in the studies used have to be acknowledged. Additionally, a Steering Group publishes a report of potential conflicts of interests based on information about external funding of Cochrane Groups. \\
In order for keeping the reviews up-to-date, they are revised in a two-year circle with exceptions. In addition to inclusion of new evidence in a field, the revision and maintenance process may as well includes change in analysis methods. This can reflect some advance in clinical science as for example new information about important subgroups, as well as new methods for conducting a Cochrane Review. However, there are no clear guidelines and the Cochrane Groups are free in the rate and extent of up-dating their reviews.

\subsection{Methods for Cochrane Reviews}
A research question defines the following points: ``the types of population (participants), types of interventions (and comparisons), and the types of outcomes that are of interest''. From the research question, usually the eligibility criteria follow. Usually, outcomes are not part of eligibility criteria, except for special cases such as adverse effect reviews. \\
The type of study is an important eligibility criterium. The Cochrane Collaboration focuses ``primarily on randomized controlled trials'', and also, the methods of study identification in literature search are focused on randomized trials. Furthermore, study characteristics such as blinding of study operators with respect to treatment and cluster-randomizing might be additional eligibility criteria which have to be chosen by the review authors. \\
After having specified the eligibility criteria, studies have to be collected. The central idea of systematic reviews, and also meta-analyses, is that the collected studies are a random sample of a population of studies, i.e. that they are representative and can be used to assess population properties. Therefore, the search process is crucial, as a selective search result may impose bias on the sample of studies available, making it a non-random sample. For this purpose, the Cochrane Groups are advised to go beyond MEDLINE !!cite!!, because a search restricted to it has been shown to deliver only 30\% to 80\% of available studies. ``Time and budget restraints require the review author to balance the thoroughness of the search with efficiency in use of time and funds and the best way of achieving this balance is to be aware of, and try to minimize, the biases such as publication bias and language bias that can result from restricting searches in different ways.'' It is important to note that not only studies, but also study reports are occasionally used in the reviews, as they may provide useful information. \\
There are different sources that are being used to search for studies. 
\begin{itemize}
\item The Cochrane Central Register of Controlled Trials is a source of reports of controlled trials. ``As of January 2008 (Issue 1, 2008), CENTRAL contains nearly 530,000 citations to reports of trials and other studies potentially eligible for inclusion in Cochrane reviews, of which 310,000 trial reports are from MEDLINE, 50,000 additional trial reports are from EMBASE and the remaining 170,000 are from other sources such as other databases and handsearching.'' It includes citations published in many languages, citations only available in conference proceedings, citations from trials registers and trials results registers.
\item MEDLINE. MEDLINE includes over 16 million references to journal articles. 5,200 journals publishing in 27 languages are indexed for MEDLINE. PubMed gives access to a free version of MEDLINE with up-to-date citations. NLM gateway such as the Health Services Research Project, Meeting Abstracts and TOXLINE Subset for toxicology citations allows for search in both databases together with additional data from the US National Library of Medicine.
\item EMBASE. 4,800 Journals publishing in 30 languages are indexed to EMBASE, which includes more than 11 million records from 1974 onward. EMBASE.com also includes 7 million unique records from MEDLINE (1966 up to date) together with its own records. Additionally, EMBASE Classic allows access to digitized records from 1947 to 1973. EMBASE and MEDLINE each have around 1,800 journals not indexed in the other database.
\item Regional or national and subject specific databases can additionally be consulted and often provide important information. Financial considerations may limit the use of such databases.
\item General search engines such as Google Scholar, Intute and Turning Research into Practice (TRIP) database can be used.
\item Citation Indexes. The database lists articles published in around 6,000 Journals with articles in which they have been cited and is available online as SciSearch. This form of search is known as cited reference searching.
\item Dissertation sources. Dissertations are often listed in MEDLINE or EMBASE but one is advised to also search in specific dissertation sources.
\item Grey Literature Databases. Approximately 10\% of the results in the Cochrane Database stems from conference abstracts and other grey literature. The Institute for Scientific and Technical Information in France provides access to entries of the previously closed System for Information on Grey Literature database of the European Association for Grey Literature Exploitation). Another source is the Healthcare Management Information Consortium (HMIC) database containing records from the Library and Information Services department of the Department of Health (DH) in England and the King's Fund Information and Library Service. The National Technical Information Service (NTIS) gives access to the results of US and non-US government-sponsored research, as well as technical report for most published results. References from newsletters, magazines and technical and annual reports in behavioral science, psychology and health are provided in the PsycEXTRA database which is linked to PsycINFO database.
\end{itemize}

\subsection{Structure and Content}
The dataset consists of 6353 systematic reviews from the Cochrane Library with 70662 studies and 744717 results. The results all stem from comparisons of a healthcare interventions or treatments to a reference. The reference may be a placebo control group or a other intervention or treatment. A result can not only be about efficacy of the treatments, but also about safety (adverse effects).\\
In Table \ref{barbiturate.row}, two results from a systematic review about barbiturates are shown as they are given in the dataset. As can be seen, further specifications are provided by the variables in the columns. \\
The \texttt{comparison.name} variable specifies \textit{what kind} of treatments or interventions are compared, the \texttt{outcome.name} variable \textit{how} it is compared, and the \texttt{subgroup.name} variable (not indicated in table) \textit{if and to what experimental subgroup} the result belongs. \\
The result is of a binary type, and the counts of events in the treatment group are in \texttt{events1} and of the control group in \texttt{events2} and the total number of participants are given in columns \texttt{total1} and \texttt{total2}. As can be seen, events denote here "death at the end of follow-up".

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(barbi1, label = "{}barbiturate.row"{}, digits = 0, caption = "{}Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted"{}): object 'barbi1' not found}}\end{kframe}

A complete listing of the variables of a result is given in Table \ref{variable}. Depending on the type of the data, \eg if it is binary or continuous, some variables are missing for the specific results.

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{l l}
      \textbf{Variable} & \textbf{Description}\\
      \hline
      \texttt{id} & An id of the review for identification purposes \\
      %\texttt{doi} & Digital object identifier. A unique id of the review such that  \\ &the full text of the review can be found on the web.\\
      % \texttt{file.index} & Internal index of the file in the Cochrane library.\\
      % \texttt{file.version} & Denotes the version of the review, since the reviews are \\ &occasionally updated.\\
      %\multicolumn{2}{c}{textbf{Study level variables}}\\ 
      \hline
      \texttt{study.name} & Name of the study to which the result belongs\\
      \texttt{study.year} & Year in which the study was published \\
      \texttt{study.data.source} & Source of the study, either ``Publ \\
      \hline
      \texttt{comparison.name/.nr} & Specification of the interventions compared in the study  \\ &and a unique number for the comparison\\
      \texttt{outcome.name/.nr} & Specification by which outcome the interventions are compared\\ &and a unique number for the outcome\\
      \texttt{subgroup.name/.nr} & Potentially indication of affiliation to subgroups and a \\ &unique number for the subgroup\\
      \texttt{outcome.measure} & Indication of the quantification method of the effect \\ &(of one intervention compared to the other).\\
      \texttt{effect} & Measure of the effect given in the quantity denoted by \\ &\texttt{outcome measure}.\\
      \texttt{se} & Standard error of the measure of the effect,\\
      \texttt{events1/events2} & The counts of patients with an outcome \textit{if}\\ &measurement/outcome is binary or dichotomous \\ &2 (1 for treatment group and 2 for control group).\\
      \texttt{total1/total2} & Number of patients in groups.\\
      \texttt{mean1/mean2} & Mean of patient measurements \textit{if} outcome is continuous.\\
      \texttt{sd1/sd2} & Standard deviation of mean \textit{if} \\ &outcome is continuous.
    \end{tabular}
  \caption{Dataset variable names and descriptions  \label{variable}}
  \label{variable}
  \end{center}
\end{table}

Results are part of studies that are again part of a (systematic) review. This structure of a review is shown in Figure \ref{review}.

\begin{figure}
\tikzstyle{every node}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\begin{tikzpicture}
[grow = right, anchor = west, 
  growth parent anchor=east, % added code
  parent anchor=east]
  \node {Review} [edge from parent fork right]
    child { node {Comparison 2}
      child { node {Outcome 2}}
      child { node {Outcome 1}
        child { node {Subgroup 2}}
        child { node {Subgroup 1}
          child  { node {Result 2}}
          child  { node {Result 1}}
          }}
    }
    child [missing] {}		
    child { node {Comparison 1  }};
\end{tikzpicture}
\caption{Structure of a hypothetical review with two different comparisons}
\label{review.structure}
\end{figure}

\vspace{0mm}
The structure of a review will now be outlined based on an example of the dataset. Let us consider the previously mentioned barbiturate and head injury review. The aim was to ``assess the effects of barbiturates in reducing mortality, disability and raised ICP (intra-cranial pressure) in people with acute traumatic brain injury'' as well as to ``quantify any side effects resulting from the use of barbiturates'' %\citep{barbiturate}. \\
%Since there are arguments for and against use of barbiturates, the authors of the review did a comprehensive literature search and collected all available study findings. 
The review comprises five studies in total. Three of them compared barbiturate to placebo, one compared barbiturate to Mannitol and one Pentobarbital to Thiopental. The studies have different outcomes, for example, death or death and severe disability at follow up, but also dropout counts or adverse effects (secondary outcomes). 
We have continuous (e.g. mean body temperature) and binary outcome data (e.g. death/no death). One study split up outcomes for patients with and without haematoma, which would be subgroups. Thus, it is important not to confuse results with studies. A study can contribute multiple results to a systematic review, for example, primary and secondary outcomes and adverse effects.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jul 11 14:21:43 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

Information about missing values in the dataset is given in Table \ref{missing}. The relative amount of missing values is low, except for study years. For continuous outcomes, the cases are counted were neither a mean difference nor means are available. Similarly, the counts of cases where neither standard errors nor standard deviations are available are provided. Study years before 1920 and after 2019 are declared as missing, as well as sample sizes equal to zero.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jul 11 14:21:43 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Neither means nor standard deviations (CONT) & 775 \\ 
  Zero participants in one group & 15162 \\ 
  Missing study publication year & 7942 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

The studies that are included in the reviews and have been published are most often from the years after 1980 (5\% quantile = 1982, 95\% quantile = 2014,). The median of the publication years is 2003, the mean 2000.97 and the quartiles are 1996 and 2008. 1075 studies have been published in 2018, none in 2019. \\
The top treatment effect measure (risk ratio, mean difference, hazard ratio etc.) abundances are summarized in Table \ref{outcome.measure.frequencies}. One can conclude of the table that roughly 31 \% of outcomes in the dataset are continuous and the rest being some sort of discrete or binary outcomes, most often binary (more than 65\%).

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jul 11 14:21:43 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrr}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
RR & 361902 & 48.6\% \\ 
  MD & 164920 & 22.1\% \\ 
  OR & 72012 & 9.7\% \\ 
  SMD & 70717 & 9.5\% \\ 
  PETO\_OR & 39710 & 5.3\% \\ 
  RD & 11068 & 1.5\% \\ 
  Hazard Ratio & 8054 & 1.1\% \\ 
  Odds Ratio & 4055 & 0.5\% \\ 
  other & 12279 & 1.6\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}
